\vspace{-1em}Guidance, please! Towards a framework for RDF-based constraint languages.

### 2015-07-16 paper/paper 2/dc-2015.tex
transformations
inverse transformations

\subsection{Constraint Transformation}

@@

>>>>

\subsection{Bidirectional Constraint Transformations}

@@

\subsection{XXX}

\begin{ex}
owl:Thing 
    spin:rule [ a sp:Construct ; sp:text """
        CONSTRUCT {            
            ?cc
                a owl:Restriction ;
                owl:minQualifiedCardinality ?cv ;
                owl:onProperty ?lp1 ;
                owl:onClass ?c1 . }
        WHERE { 
            ?this
                a rdfcv:SimpleConstraint ;
                rdfcv:contextClass ?cc ;
                rdfcv:leftProperties ?leftProperties ;
                rdfcv:classes ?classes ;
                rdfcv:constrainingElement "minimum qualified cardinality restriction" ;
                rdfcv:constrainingValue ?cv .  
            ?leftProperties 
                rdf:first ?lp1 ;
                rdf:rest rdf:nil .    
            ?classes 
                rdf:first ?c1 ;
                rdf:rest rdf:nil . } """ ; ] .
\end{ex}
